\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Ashwin Chatterji}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{www.ashwinchat.com}
% vs how you want it to show up. If it's you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://www.ashwinchat.com}
\newcommand{\yourEmail}{ashwinath@hotmail.com}
\newcommand{\githubUserName}{ashwinath}
\newcommand{\linkedInUserName}{ashwin-chatterji}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}} $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
     $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
\educationHeading{Bachelor of Business (Honours)}{Nanyang Technological University}{Singapore}{Aug 2013 - May 2016}

\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
% F5 Inc
\resumeHeading{F5, Inc}{Senior Software Engineer}{Singapore}{Aug 2023 – Present}
\begin{bullets}
    \item Served as Site Reliability Engineer (SRE) at F5 Inc., Distributed Cloud, managing production on-call responsibilities for Customer Edges (CE), Regional Edges (RE), and Global Controller (GC).
    \item Specialized in software provisioning for CEs across AWS, GCP, Azure, bare metal machines, and VMware VMs, enabling automated deployment via SaaS portal.
    \item Orchestrated end-to-end CE provisioning, including Kubernetes installation, data plane and control plane software deployment, DDoS protection, and metric/log reporting to SaaS portal.
    \item Contributed to security compliance by implementing STIGs/FIPS hardening for FedRAMP requirements.
    \item Managed CE lifecycle, including Linux OS upgrades via OSTree and remote software updates triggered by customer-initiated upgrades through the SaaS portal.
\end{bullets}
\sectionsep

% INDEED
\resumeHeading{Indeed.com}{Software Engineer}{Singapore}{Jun 2022 – Mar 2023}
\begin{bullets}
    \item Designed and implemented A/B testing frameworks to evaluate salary estimates across multiple regions and platforms, enhancing data-driven decision-making.
    \item Decomposed complex features into manageable subtasks, enabling effective onboarding and contributions from new university graduates.
\end{bullets}
\sectionsep

% GOJEK
\resumeHeading{Gojek}{Software Engineer, Infrastructure}{Singapore}{Mar 2020 – Jun 2022}
\begin{bullets}
    \item Developed batch ensembling feature in \href{https://github.com/gojek/turing}{\underline{Turing}}, leveraging Kubernetes Go client to orchestrate Spark jobs within Kubernetes clusters, improving job efficiency.
    \item Established and maintained critical infrastructure for Data Science Platform, including Prometheus, Knative, KServe, Istio, and Kubernetes clusters across multiple regions.
    \item Optimized statistical error calculations for large-scale forecast data using a distributed Ray cluster on Kubernetes, boosting performance and accuracy.
\end{bullets}
\sectionsep

% 99.co
\resumeHeading{99.co}{Backend/DevOps Engineer}{Singapore}{Jan 2018 – Feb 2020}
\begin{bullets}
    \item Built backend systems for geospatial and property data search, supporting New Launch queries with high efficiency.
    \item Enhanced autocomplete service to deliver landmark and cluster name completions in under 5 milliseconds, improving user experience.
    \item Implemented federated login system with Facebook and Google OAuth, ensuring secure and seamless user authentication.
    \item Designed automated scheduling system for Autorefresh, increasing visibility of listings in search results.
    \item Deployed automated CI/CD pipelines using Travis CI, Docker, Kubernetes, and AWS EBS.
    \item Deployed monitoring, alerting and logging systems with Prometheus, Istio Telemetry, Grafana, Fluentd, Elasticsearch and Kibana.
\end{bullets}
\sectionsep

% DXC
\resumeHeading{DXC Technology}{Software Developer}{Singapore}{Jul 2016 – Dec 2017}
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

% Financials
\projectHeading{Financials}{https://github.com/ashwinath/financials}{Go, Kubernetes, Helm}
Financials is a way to track your financial independence in Singapore's context. Inspired by ``Your Money or Your Life" by Vicki Robin. It uses a Grafana frontend to display your current assets, investments and expenditure.
\sectionsep
 
%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Languages:}{Go, Python, Java, Javascript, Typescript, Bash, SQL, \LaTeX}
    \\
    \singleItem{Development Tools:}{Tmux, Neovim, i3-gaps}
    \\
    \singleItem{Technology:}{Kubernetes, Helm, Prometheus, Linux, Git, GCP, Docker, ElasticSearch, PostgreSQL, InfluxDB}
\end{skillList}

\end{document}
